---
title: "Web Scraping ISO 3166 Country Codes"
author: "Owais"
date: "2025-03-21"
output: html_document
---
# Web Scraping ISO 3166 Country Codes

This document demonstrates how to scrape a table of ISO 3166 country codes from Wikipedia using R. The table is extracted, cleaned, and saved as a CSV file.

## Setup

First, ensure that the necessary R packages are installed and loaded. These packages include `dplyr`, `rvest`, `httr`, `jsonlite`, and `RSelenium`.

```{r warning=FALSE}
# Install required packages (if not already installed)
# install.packages("dplyr")
# install.packages("rvest")
# install.packages("httr")
# install.packages("jsonlite")
# install.packages("RSelenium")

# Load the required libraries
library(dplyr)      # For data manipulation
library(rvest)      # For web scraping
library(httr)       # For handling HTTP requests
library(jsonlite)   # For working with JSON data
library(RSelenium)  # For browser automation (if needed)
```

## Scraping the Data

The target webpage is the Wikipedia page containing the list of ISO 3166 country codes. The table is extracted using the `rvest` package.

```{r warning=FALSE}
# Define the URL of the Wikipedia page
link <- "https://en.wikipedia.org/wiki/list_of_ISO_3166_country_codes"

# Read the HTML content of the page
page <- read_html(link)

# Extract the sortable table from the page
element <- page %>% html_element("table.sortable")

# Convert the HTML table into a data frame
df <- html_table(element, header = FALSE)

# Display the first few rows of the raw data
head(df)
```

## Cleaning the Data

The extracted table contains unnecessary rows and headers. We clean the data by removing the first two rows and setting the column names.

```{r warning=FALSE}
# Set the column names using the second row of the data frame
names(df) <- df[2, ]

# Remove the first two rows (header and subheader)
df <- df[-1:-2, ]

# Display the cleaned data frame
head(df)
```

## Saving the Data

Finally, the cleaned data is saved as a CSV file for future use.

```{r warning=FALSE}
# Save the cleaned data frame as a CSV file
write.csv(df, "iso_codes.csv", row.names = FALSE)

# Confirm that the file has been saved
cat("The data has been saved as 'iso_codes.csv'.")
```

## Conclusion

This document demonstrates how to scrape, clean, and save a table of ISO 3166 country codes from Wikipedia using R. The resulting CSV file can be used for further analysis or integration into other projects.

